\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{Macallan64}The Macallan 64 Years Old in Lalique Cire Perdue,\ \url{http://us.themacallan.com/the-whisky/limited-releases/the-macallan-64-years-old-in-lalique-cire-perdue/}

\bibitem{WhiskeyDB}Whiskey Database,\ \url{http://whiskyanalysis.com/index.php/methodology-introduction/methodology-biases-and-limitations/}

\bibitem{Chivas}Whisky Advocate,\ \url{http://whiskyadvocate.com/2010/06/28/what-does-a-whiskys-age-really-mean/}

\bibitem{WhiskyDotCom}Whisky.com,\
\url{https://www.whisky.com/whisky-database/database.html}

\bibitem{WhiskyStats}Whiskeystats.net,\
\url{http://www.whiskystats.net/}

\bibitem{WhiskyAnalysis}WhiskyAnalysis.com\
\url{http://whiskyanalysis.com/}

\bibitem{WhiskyMaps}Whiskybase.com Maps,\
\url{https://www.whiskybase.com/maps}

\bibitem{Finney}D. J. Finney,\
On the distribution of a variate whose logarithm is normally distributed,\ J. Roy. Statist. Soc. Ser. B, \textbf{7} (1941), pp. 155-161

\bibitem{Shen}Wei-Hsiung Shen,\
Estimation of Parameters of a Lognormal Distribution,\ Taiwanese Journal of Mathematics,\ Vol.2, No. 2, pp. 243-250, June 1998

\bibitem{KLWines}K\&L Wines,The Glenlivet 12 Year Old\
\url{http://www.klwines.com/p/i?i=620004}

\bibitem{Thrillist}Thrillist,10 Scotches Under \$50 That You Should Be Drinking\
\url{https://www.thrillist.com/vice/best-scotch-whisky-under-50-johnnie-walker-glenlivet-laphroaig}

\bibitem{StatisticsDoneWrong}Reinhart, Alex (2015). \textit{Statistics Done Wrong}.
San Francisco:\
No Starch Press, Inc.

\bibitem{GitHub}Detweiler, Brian. MATH 8756 Final Project,\
\url{https://github.com/bdetweiler/math-8756-final-project}

\end{thebibliography}

